%-------------------------
% Resume in Latex (duplicated and adapted)
% Author : Generated from example.tex
%------------------------

\documentclass{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage{tabularx}
\usepackage{ragged2e} % justify
\input{glyphtounicode}

%----------FONT OPTIONS----------
% Use a commonly available font package to improve compile compatibility.
\usepackage{lmodern}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{3.60004pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands (same as template)
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{0pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape MAISSA DRIRA} \\ \vspace{12pt}
    Software Engineering Student \\ \vspace{6pt}
     +216 55 845 445 $ | $ \href{mailto:maissa.drira1@gmail.com}{\underline{maissa.drira1@gmail.com}} $ | $ 
    \href{https://linkedin.com/}{{Linkedin (\underline{https://www.linkedin.com/in/drira-maissa-220689220/})}} $ | $
    \href{https://github.com/}{{Github (\underline{https://github.com/maissa0})}} $ | $ \href{https://portfolio-maissa-drira.vercel.app/}{{Portfolio (\underline{https://portfolio-maissa-drira.vercel.app/})}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\justifying
Final-year Software Engineering student and Technology Enthusiast with C1-level English and French proficiency and a strong background in advanced full-stack development. Experienced in building responsive ,data-driven apps and currently \textbf{seeking a final-year software engineering internship}.



%-----------CERTIFICATIONS-----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{\textbf{Angular - The Complete Guide (2025 Edition)} --- Udemy \hfill    November 6, 2025 \hfill }}
  \small{\item{\textbf{Hashgraph Developer Course} --- The Hashgraph Association \hfill November 6, 2025 \hfill }}
  \small{\item{\textbf{AWS Academy Graduate - Cloud Foundations} --- AWS Academy \hfill November 5, 2025 \hfill }}
\end{itemize}

%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Internship: Multi-Tenant SaaS CRM Platform Development}{Jun. 2025 - Aug. 2025}
      {Alwen.co | Tunis, Tunisia}{}
    \resumeItemListStart
        \resumeItem{Developed an enterprise-level Multi-Tenant SaaS CRM solution using Odoo v18 (backend) and Flutter Web (frontend).}
        \resumeItem{Built backend modules for automated CRM deployment and strict tenant-level data isolation.}
        \resumeItem{Employed Agile-inspired workflows and continuous testing.}
        \resumeItem{Technologies: Odoo v18, PostgreSQL, Flutter for Web, JSON-RPC, Riverpod, GoRouter.}
    \resumeItemListEnd

    \resumeSubheading
      {Internship: Smart Exam - Academic Anomaly Detection}{Jul. 2024 - Aug. 2024}
      {DSI, ESPRIT | Ariana, Tunisie}{}
    \resumeItemListStart
        \resumeItem{Developed a full-stack web application to detect anomalies in student grades and enhance educational processes.}
        \resumeItem{Technologies: React JS, Spring Boot (microservices), PostgreSQL.}
    \resumeItemListEnd

    \resumeSubheading
      {Internship: Initiation}{Aug. 2022}
      {Attijari Bank Agency | Ariana, Tunisie}{}
    \resumeItemListStart
        \resumeItem{Welcomed and oriented clients. }
        \resumeItem{Managed administrative tasks including data entry and document digitization.}
        \resumeItem{Assisted staff with daily operations, demonstrating adaptability and teamwork.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------ACADEMIC PROJECTS-----------
\section{Academic Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {CruxHire - AI-Powered Recruitment Platform}{2024 - 2025}
          \resumeItemListStart
            \resumeItem{Developed an AI-powered recruitment platform automating talent acquisition with built-in AI for skill-based matching.}
            \resumeItem{Designed for scalability, integrating Google OAuth, Stripe, and AWS S3 for storage.}
            \resumeItem{Technologies: Next.js 15, React 19, TypeScript, Prisma/PostgreSQL, Groq SDK, AWS Amplify/S3, Docker.}
          \resumeItemListEnd

      \resumeProjectHeading
          {Meetzy - Event Management Platform}{2023 - 2024}
          \resumeItemListStart
            \resumeItem{Built a modern, full-stack event management platform with integrated secure payments (Stripe) and user authentication (Clerk).}
            \resumeItem{Technologies: Next.js 14, TypeScript, Node.js, MongoDB/Mongoose.}
          \resumeItemListEnd

      \resumeProjectHeading
          {L'EARN - E-Learning and Recruitment Platform}{2024 - 2025}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web application combining e-learning and job recruitment.}
            \resumeItem{Technologies: Angular, Spring Boot (microservices), MySQL, OpenAI API.}
          \resumeItemListEnd


     
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Integrated Engineering Cycle in Computer Science}{Sept. 2021 - Present}
      {l'\'Ecole Sup\'erieure Priv\'ee d'Ing\'enierie et de Technologies (ESPRIT) | Ariana, Tunisie}{}

    \resumeSubheading
      {High School Diploma (Baccalaur\'eat) in Mathematics}{Sept. 2020 - Jul. 2021}
      {l'\'Ecole Sup\'erieure Priv\'ee d'Ing\'enierie et de Technologies (ESPRIT) | Ariana, Tunisie}{}
  \resumeSubHeadingListEnd
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills \& Tools}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Languages \& Frameworks:} Next.js 15, React 19, Angular, TypeScript, Tailwind CSS, shadcn/ui, Spring Boot (Microservices), Node.js, Symfony 5, Odoo v18, Java 17, JavaFX 20, Flutter (Web), C, C++, PHP 7, JavaScript \\
        \textbf{Databases \& Cloud:} PostgreSQL, MySQL, MongoDB, Mongoose, Prisma, SQL, PLSQL, Oracle 11, AWS (S3, Amplify, Cloud Foundations), Docker, GitHub Actions \\
        \textbf{AI, APIs \& Tools:} Groq SDK, AWS Bedrock/Textract, OpenAI API, Auth.js, Clerk, Stripe, Resend, Nodemailer, UploadThing \\
        \textbf{State Management / Routing:} Zustand, Riverpod, GoRouter \\
        \textbf{Methodologies:} Agile/Scrum, Continuous Testing, Documentation
    }}
\end{itemize}
%-----------LANGUAGES & SOFT SKILLS-----------
\section{Languages \& Soft Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{\textbf{Languages:} French: C1 \hspace{15pt}$|$\hspace{1pt} English: C1} }
    \small{\item{\textbf{Soft Skills:} Teamwork, Problem-solving, Communication, Project management (Scrum), Mentoring, Punctual and Organized}}
 \end{itemize}

%-------------------------------------------
\end{document}
